Cross-national analyses require additional controls to account for the non-independence of nations

### 2023-07-10 manuscript.tex
add zenodo doi citation

All data and code are accessible on GitHub (\url{https://github.com/ScottClaessens/crossNationalCorrelations}). We used the targets R package\textsuperscript{94} to create a reproducible data analysis pipeline and the papaja R package\textsuperscript{95} to reproducibly generate the manuscript.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Landau2021}{}}%
\CSLLeftMargin{94. }%
\CSLRightInline{Landau, W. M. \href{https://doi.org/10.21105/joss.02959}{The targets {R} package: A dynamic {M}ake-like function-oriented pipeline toolkit for reproducibility and high-performance computing}. \emph{Journal of Open Source Software} \textbf{6}, 2959 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Aust2020}{}}%
\CSLLeftMargin{95. }%
\CSLRightInline{Aust, F. \& Barth, M. \emph{\href{https://github.com/crsh/papaja}{{papaja}: {Create} {APA} manuscripts with {R Markdown}}}. (2020).}

>>>>

All data and code are accessible on GitHub (\url{https://github.com/ScottClaessens/crossNationalCorrelations})\textsuperscript{94}. We used the targets R package\textsuperscript{95} to create a reproducible data analysis pipeline and the papaja R package\textsuperscript{96} to reproducibly generate the manuscript.

@@

\leavevmode\vadjust pre{\hypertarget{ref-github}{}}%
\CSLLeftMargin{94. }%
\CSLRightInline{Claessens, S., Kyritsis, T. \& Atkinson, Q. D. Cross-national analyses require additional controls to account for the non-independence of nations - ScottClaessens/crossNationalCorrelations: v1.0.0. (2023) doi:\href{https://doi.org/10.5281/zenodo.8128702}{10.5281/zenodo.8128702}.}

\leavevmode\vadjust pre{\hypertarget{ref-Landau2021}{}}%
\CSLLeftMargin{95. }%
\CSLRightInline{Landau, W. M. \href{https://doi.org/10.21105/joss.02959}{The targets {R} package: A dynamic {M}ake-like function-oriented pipeline toolkit for reproducibility and high-performance computing}. \emph{Journal of Open Source Software} \textbf{6}, 2959 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Aust2020}{}}%
\CSLLeftMargin{96. }%
\CSLRightInline{Aust, F. \& Barth, M. \emph{\href{https://github.com/crsh/papaja}{{papaja}: {Create} {APA} manuscripts with {R Markdown}}}. (2020).}
